Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-24 paper/paper.tex
amanda's latest airplane systems engineering

Our team was divided by area of expertise into a mechanical team and an electrical team.
The mechanical team began the year with the goal of producing two competition worthy airframes. These were to become the \emph{Daedalus} and \emph{Knight Two}.

We determined, after consulting with R/C experts, that a high wing trainer is the most stable and proven fixed-wing design. Trainers traditionally have light wing loading for slow speed flight, and will be able to carry payload

One of the most difficult design decisions was to quantify ``ample payload.'' The payload size and weight is the major determining factor in the aircraft size.
% -- amanda will finish this by mon noon: 
We started off assuming an electronics (computer + batteries) payload of 2.5lbs and a pan-tilt camera of 2.5lbs and 8 inch diameter.

>>>>

Our team was divided by area of expertise into a mechanical team and an electrical team.The mechanical team began the year with the goal of producing two competition worthy airframes. These were to become the \emph{Daedalus} and \emph{Knight Two}.

The teams made design decisions based on the aforementioned competition goals.

One of the most difficult design decisions was to quantify ``ample payload.'' Payload size and weight is the major determining factor in aircraft size.  We originally assumed a 2.5lb electronics (computer + batteries) payload and a 2.5lb pan-tilt camera 8'' in diameter, requiring 6'' of vertical space extruding from the bottom of the aircraft. These considerations introduced two major design parameters: the aircraft must be capable of carrying a minimum 5lb payload, and must be situated to provide clearance for the pan tilt unit.

Additionally, we sought an easily controllable, stable platform to accommodate the autopilot, and an ability to fly at low speeds, in order to more easily capture clear images.

We determined, after consulting with R/C experts, that a high wing trainer is the most stable and proven fixed-wing design. Trainers traditionally have light wing loading for slow speed flight, and are able to carry a comparatively large payload. Additionally, a large plane with lower wing loading is easier to control, and easier to recover if power is lost. Consciously agreeing to err on the side of caution, we sought a large plane capable of accommodating a worst-case scenario payload, and settled on a wingspan on the order of 10'-12'. Though lighter and smaller payload alternatives were found as the year progressed, these merely leave us with more freedom for future modifications.
%That last sentence sounds kind of eh, I'm stuck on a decent wording, so I'm leaving it for now.

The decision to employ a large, high wing trainer, however, forced us to rethink our original pan-tilt design. Last year, in order to accommodate the pan-tilt unit, we designed a pusher plane, enabling us to mount the pan-tilt under the plane's nose, which had sufficient clearance. Since trainers are generally designed with front-mounted engines (I presume?), we were forced to engineer a new solution requiring significantly less clearance. In the long run, we modified the pan-tilt mount to allow us to recess more of the pan-tilt unit into the body of the plane---this had the added benefit of providing more protection to an expensive piece of equipment on takeoff and landing.
